\documentclass[10pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Chaochen Wang - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Chaochen Wang:  CV (Curriculum Vitae)},
            pdfauthor={Chaochen Wang},
            pdfkeywords={RMarkdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Chaochen Wang}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Senior Associate}

\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:chaochen@wangcc.me}{\nolinkurl{chaochen@wangcc.me}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  +81
90-6592-0459  \hspace{1 mm}     \faGlobe \hspace{1 mm} \href{http://wangcc.me}{\tt wangcc.me}    | \emph{Updated:} \today}

\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{EDUCATION}\label{education}}

\textbf{London School of Hygiene \& Tropical Medicine}, MSc of Medical
Statistics, Distinction Degree \hfill 2018.9

\textbf{Nagoya University Graduate School of Medicine}, Doctor of
Philosophy (Medical Science) \hfill  2016.3

\textbf{Nagoya University Graduate School of Medicine}, Master of
Medical Science \hfill 2013.3

\textbf{Shanghai Jiaotong Univeristy}, B.S. Nutrition Science
\hfill 2010.7

\hypertarget{career-history}{%
\section{CAREER HISTORY}\label{career-history}}

\textbf{Japan Value, Evidence and Outcomes, Japan Drug Development and
Medical Affairs (JDD\&MA), Eli Lilly and Company Japan K.K.}

\begin{quote}
Senior Associate \hfill 2021.10--present
\end{quote}

\hypertarget{responsibility-health-technique-assessment-hta-real-world-evidence-rwe-generation.}{%
\subsection{Responsibility: Health technique assessment (HTA), Real
world evidence (RWE)
generation.}\label{responsibility-health-technique-assessment-hta-real-world-evidence-rwe-generation.}}

\textbf{Department of Public Health, Aichi Medical University School of
Medicine:}

\begin{quote}
Assistant Professor \hfill 2015.4--2021.9
\end{quote}

\hypertarget{responsibility-teaching-and-research}{%
\subsection{Responsibility: teaching and
research}\label{responsibility-teaching-and-research}}

\begin{itemize}
\tightlist
\item
  Working closely with the professors and other colleagues mainly in
  epidemiology of gastroenterological cancer
\item
  Responsible for statistical consulting from medical doctors in the
  university hospital
\item
  Responsible for education to undergraduate medical students on
  statistical methods used in medical researches
\item
  Cooperating with medical doctors in hospital university on projects
  studying locomotive syndrome
\end{itemize}

\hypertarget{projects}{%
\subsection{Projects:}\label{projects}}

\begin{itemize}
\tightlist
\item
  Data analysis using large scale cohort studies such as the Japan
  Collaborative Cohort Study, literature meta-analysis, the UK National
  Diet and Nutrition Survey Rolling Program data, and data provided by
  doctors in Aichi Medical University hospital
\item
  All projects and publications were conducted under Linux environment
  such as Ubuntu OS with R, STATA, and/or Python language
\item
  Presented in the World Congress of Epidemiology in Alaska (2014) as
  well as in Saitama (2017) as poster presentations
\item
  Recent research on the day-time patterns of carbohydrate intake using
  the UK national Diet and Nutrition Survey data was accepted as oral
  presentation in the 13th European Nutrition Conference in Dublin,
  Ireland 2019
\end{itemize}

\textbf{Clinical Study Support:}

\begin{quote}
Part-time Researcher (8h/w) \hfill 2018.10--2021.6
\end{quote}

\hypertarget{responsibility-statistical-analysis-training-of-the-analysis-team}{%
\subsection{Responsibility: statistical analysis, training of the
analysis
team}\label{responsibility-statistical-analysis-training-of-the-analysis-team}}

\begin{itemize}
\tightlist
\item
  Experience in producing statistical analysis plan (SAP) for clinical
  and observational studies; conducted detailed comparisons and results
  calculation on cancer survival from hospital clients; performed
  database analyses through commercial medical databases such as Medical
  Database Vision.
\item
  Organizing statistical study seminars to train the team members and
  learn the latest statistical knowledge and skills for on-going and
  future study projects
\end{itemize}

\textbf{Real World Data Co., Ltd.:}

\begin{quote}
Sub-contracted Researcher \hfill 2021.1--2021.8
\end{quote}

\hypertarget{responsibility-statistical-analysis-medical-writing-quality-check-statistical-analysis-seminar-lecturer}{%
\subsection{Responsibility: statistical analysis, medical writing
quality check, statistical analysis seminar
lecturer}\label{responsibility-statistical-analysis-medical-writing-quality-check-statistical-analysis-seminar-lecturer}}

\begin{itemize}
\tightlist
\item
  Experience in producing statistical analysis plan (SAP), perform
  analysis, and result presentation for descriptive statistical analysis
  on COVID-19 patients using large scale database that include
  electronic medial records (EMR) and medical expenses claim.
\item
  Enrolled as a seminar lecturer for a commercial seminar entitled ``To
  maximize the usage of database research - study design and statistical
  analysis'', and responsible for the SAS practical session.
\item
  Providing professional medical manuscript writing quality check.
\end{itemize}

\hypertarget{publications}{%
\section{PUBLICATIONS}\label{publications}}

\begin{itemize}
\tightlist
\item
  \textbf{*Wang, C.}, Yatsuya, H., Tamakoshi, K., Uemura, M., Li, Y.,
  \emph{et al.} 2013. Positive association between high-sensitivity
  C-reactive protein and incidence of type 2 diabetes mellitus in
  Japanese workers: 6-year follow-up. \textbf{Diabetes Metab Res Rev}
  29, 398--405.
\end{itemize}

\begin{itemize}
\item
  \textbf{*Wang, C.}, Yatsuya, H., Tamakoshi, K., Iso, H., Tamakoshi,
  A., 2015. Milk drinking and mortality: findings from the Japan
  collaborative cohort study. \textbf{J Epidemiol} 25, 66--73.
\item
  \textbf{*Wang, C.}, Yatsuya, H., Tamakoshi, K., Toyoshima, H., Wada,
  K., \emph{et al.} 2015. Association between parental history of
  diabetes and the incidence of type 2 diabetes mellitus differs
  according to the sex of the parent and offspring's body weight: A
  finding from a Japanese worksite-based cohort study. \textbf{Prev Med}
  81, 49--53.
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{*Wang, C.}, Yatsuya, H., Li, Y., Ota, A., Tamakoshi, K.,
  \emph{et al.} 2016. Prospective study of seaweed consumption and
  thyroid cancer incidence in women: the Japan collaborative cohort
  study. \textbf{Eur J Cancer Prev} 25, 239--245.
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{*Wang, C.}, Chiang, C., Yatsuya, H., Hilawe, E.H., Ikerdeu,
  E., \emph{et al.} 2017. Descriptive Epidemiology of Hypertension and
  its Association with Obesity: Based on the WHO STEPwise Approach to
  Surveillance in Palau. \textbf{Asia Pac J Public Health} 29, 278--287.
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{*Wang, C.}, Nishiyama, T., Kikuchi, S., Inoue, M., Sawada, N.,
  Tsugane, S., Lin, Y., 2017. Changing trends in the prevalence of
  \emph{H. pylori} infection in Japan (1908--2003): a systematic review
  and meta-regression analysis of 170,752 individuals. \textbf{Sci Rep}
  7, 15491.
\end{itemize}

\begin{itemize}
\item
  \textbf{*Wang, C.}, Almoosawi, S., \& Palla, L., 2019. ``Day-Time
  Patterns of Carbohydrate Intake in Adults by Non-Parametric
  Multi-Level Latent Class Analysis---Results from the UK National Diet
  and Nutrition Survey (2008/09--2015/16),'' \textbf{Nutrients},
  vol.~11, no. 10, p.~2476.
\item
  \textbf{*Wang, C.}, Ikemoto, T., Hirasawa, A., Arai, Y.-C., Kikuchi,
  S. and Deie, M., 2020. Assessment of locomotive syndrome among older
  individuals: a confirmatory factor analysis of the 25-question
  Geriatric Locomotive Function Scale. \textbf{PeerJ}, 8, e9026.
\item
  \textbf{*Wang, C.}, Yatsuya, H., Lin, Y., Sasakabe, T., Kawai, S.,
  Kikuchi, S., Iso, H. and Tamakoshi, A., 2020. Milk Intake and Stroke
  Mortality in the Japan Collaborative Cohort Study---A Bayesian
  Survival Analysis. \textbf{Nutrients}, 12, 2743.
\item
  Kawai, S., \textbf{*Wang, C.}, Lin, Y., Sasakabe, T., Okuda, M., \&
  Kikuchi, S. 2022. Lifetime incidence risk for gastric cancer in the
  Helicobacter pylori‐infected and uninfected population in Japan: A
  Monte Carlo simulation study. \textbf{International Journal of
  Cancer}, 150(1), 18-27.
\item
  Lin, Y., \textbf{*Wang, C.}, Kikuchi, S., Akita, T., Tanaka, J., Abe,
  S. K., \ldots{} \& Cancer PAF Japan Collaborators. 2021. Burden of
  cancer attributable to infection in Japan in 2015. GHM open, 1(2),
  63-69.
\item
  \textbf{*Wang, C.}, Almoosawi, S., \& Palla, L. 2021. Relationships
  Between Food Groups and Eating Time Slots According to Diabetes Status
  in Adults From the UK National Diet and Nutrition Survey (2008--2017).
  Frontiers in nutrition, 8.
\item
  Li Y, Yatsuya H, \textbf{*Wang, C.}, Uemura M, Matsunaga M, He Y,
  Khine M, Ota A. 2022. Dietary Patterns Derived from Reduced Rank
  Regression Are Associated with the 5-Year Occurrence of Metabolic
  Syndrome: Aichi Workers' Cohort Study. Nutrients; 14(15):3019
\end{itemize}

\hypertarget{awards-sholarships}{%
\section{AWARDS \& SHOLARSHIPS}\label{awards-sholarships}}

\textbf{Outstanding Graduates of Shanghai Jiaotong University}
\hfill 2010

Recipient of \textbf{Ajinomoto Scholarship} for outstanding students
from overseas \hfill 2011-2012

\textbf{Young Investigator's Award}, The 48th Annual Meeting of the
Japanese Society of Cardiovascular Disease Prevention, Tokyo
\hfill  2012

Recipient of scholarship from \textbf{Otsuka Toshimi Scholarship
Foundation} \hfill 2013-2014

\textbf{Best Reviewer} of Journal of Epidemiology \hfill 2021.1.28

\hypertarget{languages}{%
\section{LANGUAGES}\label{languages}}

\begin{itemize}
\tightlist
\item
  Chinese Mandarin: Native Speaker
\item
  Chinese Hokkien: Native Speaker
\item
  English: Fluent (IELTS overall: 8; L 8.5, R 8.5, W 7, S 7) - 2017.1.7
\item
  Japanese: Advanced (Japanese Language Proficiency Level 1)
\end{itemize}

\end{document}
